Considering scale in multilayer animal social networks

### 2020-06-11 paper/manuscript.Rmd
start layers

### Network types and construction
We generated a multilayer social network consisting `r DT[, uniqueN(get(idcol))]`
individual nodes and two aspects (season and land cover). Two season
elementary-layers (summer and winter) and three land cover elementary-layers
(forage, forest, and open) combined for a total of six layers. Single layers were
composed of individuals linked by social associations, for each season and land cover combination. Proximity-based social
network layers were generated using the R package `spatsoc` [@Robitaille_2019]
in `r version$version.string` [@R_Core_Team_2019].

Within each layer, we assumed individuals were associating if simultaneous GPS
fixes, i.e., recorded within 5 minutes of each other, were within a given
spatial distance of one another. Typically for ungulates and other gregarious
mammals, the ‘chain rule’ is applied for group assignment. For GPS data, the
chain rule is applied if discrete spatiotemporal GPS fixes buffered by a given
distance formed a contiguous buffer for two or more individuals, even if some
individuals within the buffer were not within the given distance of one another
[@Robitaille_2019]. Group assignment based on the chain rule has previously been
applied to caribou at a distance of 50 m [@Peignier_2019; @Lesmerises_2018]. In
all networks, individual caribou were represented as nodes, associations between
individuals in a given habitat type and season were represented as intralayer
edges, and connections between the same individuals across seasons and within
habitat classes were represented as interlayer edges (Figure \@ref(fig:ml)) .
<!-- eg this is connecting contexts used to calculate layer similarity -->

@@

where x is the number of fixes where individuals A and B were within a given
distance of each other, $y_{A}$ is the number of fixes from individual A when
individual B did not have a simultaneous fix, $y_{B}$ is the number of fixes
from individual B when individual A did not have a simultaneous fix, and
$y_{AB}$ is the number of simultaneous fixes from individuals A and B that were
separated by more than the given distance [@Farine_2015]. Social groups were
designated if two or more individuals occurred within a given distance of one
another at any given time point.

@@

We modified the distance threshold, hereafter the social <!--distance-->threshold, required for
group assignment using `spatsoc` [@Robitaille_2019] and re-assigned groups at
incremental distances between 5 - 500 m. For example, at the finest social
scale, only individuals within 5 m of one another were considered in the same
group, whereas at the coarsest social scale, individuals within 500 m of one
another were considered in the same group. We assumed these scales represented
visual (short distance) to auditory (long distance) sensory modalities of
caribou.

>>>>

### Network layer construction
<!--We generated a multilayer social network consisting `r DT[, uniqueN(get(idcol))]`
individual nodes and two aspects (season and land cover). Two season
elementary-layers (summer and winter) and three land cover elementary-layers
(forage, forest, and open) combined for a total of six layers. Single layers were
composed of individuals linked by social associations, for each season and land cover combination. Proximity-based social
network layers were generated using the R package `spatsoc` [@Robitaille_2019]
in `r version$version.string` [@R_Core_Team_2019].-->

<!-- TODO: better lead in -->
Within each layer, we generated proximity-based social networks using the R package `spatsoc` [@Robitaille_2019] in `r version$version.string` [@R_Core_Team_2019]. We 
assumed individuals were associating if simultaneous GPS
fixes, i.e., recorded within 5 minutes of each other, were within the spatial distance 
threshold of one another. Typically for ungulates and other gregarious
mammals, the ‘chain rule’ is applied for group assignment. <!-- TODO: simplify here-->For GPS data, the
chain rule is applied if discrete spatiotemporal GPS fixes buffered by a given
distance formed a contiguous buffer for two or more individuals, even if some
individuals within the buffer were not within the given distance of one another
[@Robitaille_2019]. Group assignment based on the chain rule has previously been
applied to caribou at a distance of 50 m [@Peignier_2019; @Lesmerises_2018]. In
all networks, individual caribou were represented as nodes, associations between
individuals in a given habitat type and season were represented as intralayer
edges, and connections between the same individuals across seasons and within
habitat classes were represented as interlayer edges (Figure \@ref(fig:ml)) .
<!-- eg this is connecting contexts used to calculate layer similarity -->

@@

where x is the number of fixes where individuals A and B were within a given
distance of each other, $y_{A}$ is the number of fixes from individual A when
individual B did not have a simultaneous fix, $y_{B}$ is the number of fixes
from individual B when individual A did not have a simultaneous fix, and
$y_{AB}$ is the number of simultaneous fixes from individuals A and B that were
separated by more than the given distance [@Farine_2015]. <!-- TODO: rm repeat?-->Social groups were
designated if two or more individuals occurred within a given distance of one
another at any given time point.

@@

We modified the distance threshold, hereafter the social <!--distance-->threshold, required for
group assignment using `spatsoc` [@Robitaille_2019] and re-assigned groups at
incremental distances between 5 - 500 m. For example, at the finest social
scale, only individuals within 5 m of one another were considered in the same
group, whereas at the coarsest social scale, individuals within 500 m of one
another were considered in the same group. We assumed these scales represented
visual (short distance) to auditory (long distance) sensory modalities of
caribou. <!-- TODO: clarify not attempting ML with multiple behaviours -->
